\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-05-06 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
Final Merge from branch 'full_aniso_kernels_matharu' to master. Anisotropy arrays are allocated only if the corresponding flag is set to true.

\begin{itemize}
\item The adjoint simulation is launched together with the back reconstruction
of the original forward wavefield from the state variables saved from
the previous forward simulation, and the finite-frequency kernels
are computed by the interaction of the reconstructed forward wavefield
and the adjoint wavefield.
\item The back-reconstructed seismograms at the original station locations
are saved to the \texttt{LOCAL\_PATH} at the end of the kernel simulations,
and can be collected to the local disk.
\item These back-constructed seismograms can be compared with the time-reversed
original seismograms to assess the accuracy of the backward reconstruction,
and they should match very well.
\item The arrays for density, P-wave speed and S-wave speed kernels are
also saved in the \texttt{LOCAL\_PATH} with the names \texttt{proc??????\_rho(alpha,beta)\_kernel.bin},
where \texttt{proc??????} represents the processor number, \texttt{rho(alpha,beta)}
are the different types of kernels.
\end{itemize}
\end{enumerate}
In general, the three steps need to be run sequentially to assure
proper access to the necessary files. If the simulations are run through
some cluster scheduling system (e.g., LSF), and the forward simulation
and the subsequent kernel simulations cannot be assigned to the same
set of computer nodes, the kernel simulation will not be able to access
the database files saved by the forward simulation. Solutions for
this dilemma are provided in Chapter~\ref{cha:Scheduler}. Visualization
of the finite-frequency kernels is discussed in Section~\ref{sec:Finite-Frequency-Kernels}.

>>>>

\begin{itemize}
\item The adjoint simulation is launched together with the back reconstruction
of the original forward wavefield from the state variables saved from
the previous forward simulation, and the finite-frequency kernels
are computed by the interaction of the reconstructed forward wavefield
and the adjoint wavefield.
\item The back-reconstructed seismograms at the original station locations
are saved to the \texttt{LOCAL\_PATH} at the end of the kernel simulations,
and can be collected to the local disk.
\item These back-constructed seismograms can be compared with the time-reversed
original seismograms to assess the accuracy of the backward reconstruction,
and they should match very well.
\item The arrays for density, P-wave speed and S-wave speed kernels are
also saved in the \texttt{LOCAL\_PATH} with the names \texttt{proc??????\_rho(alpha,beta)\_kernel.bin},
where \texttt{proc??????} represents the processor number, \texttt{rho(alpha,beta)}
are the different types of kernels.
\end{itemize}

\item \textbf{Run the anisotropic kernel simulation}

Instead of the kernels for the isotropic wave speeds, you can also
compute the kernels for the 21 independent components $C_{IJ},\, I,J=1,...,6$
(using Voigt's notation) of the elastic tensor in the cartesian coordinate system. 
This is done by setting \texttt{ANISOTROPIC\_KL} \texttt{=} \texttt{.true.} 
in \texttt{constants.h} before compiling the package. The definition of the parameters 
$C_{IJ}$ in terms of the corresponding components $c_{ijkl},ijkl,i,j,k,l=1,2,3$ of 
the elastic tensor in cartesian coordinates follows \citet{ChTr07}. The 21 anisotropic 
kernels are saved in the \texttt{LOCAL\_PATH} in one file with the name of 
\texttt{proc??????\_cijkl\_kernel.bin} (with \texttt{proc??????} 
the processor number). The output kernels correspond to absolute perturbations 
$\delta C_{IJ}$ of the elastic parameters and their unit is in $s/GPa/km^{3}$. 
For consistency, the output density kernels with this option turned on 
are for a perturbation $\delta\rho$ (and not $\frac{\delta\rho}{\rho}$) and their unit
is in s / (kg/m$^{3}$) / km$^{3}$. These `primary' anisotropic kernels
can then be combined to obtain the kernels for different parameterizations of anisotropy. 
This can be done, for example, when combining the kernel files from slices into one mesh file 
(see Section~\ref{sec:Finite-Frequency-Kernels}).

If \texttt{ANISOTROPIC\_KL} \texttt{=} \texttt{.true.} by additionally setting \texttt{ANISOTROPIC\_KL} 
\texttt{=} \texttt{.true.} in \texttt{constants.h} the package will save anisotropic kernels paramterized
as velocities related to transverse isotropy based on the the Chen and Tromp parameters \citet{ChTr07}.
The kernels are saved as relative perturbations for horizontal and vertical P and S velocities, $\alpha_{v},
\alpha_{h}, \beta_{v}, \beta_{h}$. Explicit relations can be found in appendix B. of \citet{SiLiTrTr07b}

The anisotropic kernels are only currently available for CPU mode.

In general, the three steps need to be run sequentially to assure
proper access to the necessary files. If the simulations are run through
some cluster scheduling system (e.g., LSF), and the forward simulation
and the subsequent kernel simulations cannot be assigned to the same
set of computer nodes, the kernel simulation will not be able to access
the database files saved by the forward simulation. Solutions for
this dilemma are provided in Chapter~\ref{cha:Scheduler}. Visualization
of the finite-frequency kernels is discussed in Section~\ref{sec:Finite-Frequency-Kernels}.
